Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-13 ccppabc/text/revision/main.tex
Issue #22 addressed; darkgreen text commented out.

{\bf \color{dred}
In addition to not requiring accurate covariance matrix estimates, forward models 
of the ABC-PMC method, in principle, also have the advantage that they can account 
for sources of systematic uncertainties that affect observations. All observations 
suffer from significant systematic effects which are often difficult to correct. 
For instance, in SDSS-III BOSS~\citep{Dawson:2013a}, fiber collisions and redshift
failures siginifcantly bias measurements and analysis of observables such as 
$\xigg$ or the galaxy powerspectrum~\citep{Ross:2012aa, Guo:2012a, Hahn:2017a}. 
In parameter inference, these systematics can affect the likelihood, and thus any 
analysis that requires writing down the likelihood, in unknown ways. With a forward generative model of the ABC-PMC 
method, the systematics can be simulated and marginalized out to achieve unbiased 
constraints. 
} 
{\bf \color{darkgreen} 
CHH: @MJV I incorporated the sentence into the paragraph. Can you check it out
and confirm it's fine?
} 
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, accounts for sample variance. In principle, they also have the advantage that they can account for sources of systematic uncertainties in the observational data. 
%Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix estimate that captures the sample variance of the data. While we are able to do this accurately within the scope of the HOD framework, for more general LSS parameter inference situations, it is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs, which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein).  Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a covariance matrix estimate; hence it does not face these problems.

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). As we explain throughout 
the paper, the likelihood function in LSS {\em cannot} be Gaussian. For $\xigg$, 
the correlation function must satisfy non-trivial positive-definiteness requirements 
and hence the Gaussian pseudo-likelihood function assumption is not correct 
in detail. In the case $\gmf(N)$ is used as a summary statistic
of a galaxy catalog, assuming a Gaussian functional form for the likelihood
clearly misrepresents the true likelihood function. In fact, this incorrect 
likelihood, may explain why the constraints on $\alpha$ are less biased for 
the ABC-PMC analysis than the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}
{\bf \color{darkgreen}
CHH: @MJV, I parrot a lot of arguments made in the intro without providing much extra 
'meat'. Let me know what you think. 
}

>>>>

{\bf \color{dred}
In addition to not requiring accurate covariance matrix estimates, forward models 
of the ABC-PMC method, in principle, also have the advantage that they can account 
for sources of systematic uncertainties that affect observations. All observations 
suffer from significant systematic effects which are often difficult to correct. 
For instance, in SDSS-III BOSS~\citep{Dawson:2013a}, fiber collisions and redshift
failures siginifcantly bias measurements and analysis of observables such as 
$\xigg$ or the galaxy powerspectrum~\citep{Ross:2012aa, Guo:2012a, Hahn:2017a}. 
In parameter inference, these systematics can affect the likelihood, and thus any 
analysis that requires writing down the likelihood, in unknown ways. With a forward generative model of the ABC-PMC 
method, the systematics can be simulated and marginalized out to achieve unbiased 
constraints. 
} 
%{\bf \color{darkgreen} CHH: @MJV I incorporated the sentence into the paragraph. Can you check it out and confirm it's fine?  } 
%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, accounts for sample variance. In principle, they also have the advantage that they can account for sources of systematic uncertainties in the observational data. 
%Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix estimate that captures the sample variance of the data. While we are able to do this accurately within the scope of the HOD framework, for more general LSS parameter inference situations, it is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs, which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein).  Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a covariance matrix estimate; hence it does not face these problems.

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). As we explain throughout 
the paper, the likelihood function in LSS {\em cannot} be Gaussian. For $\xigg$, 
the correlation function must satisfy non-trivial positive-definiteness requirements 
and hence the Gaussian pseudo-likelihood function assumption is not correct 
in detail. In the case of $\gmf(N)$, assuming a Gaussian functional form for 
the likelihood, which in reality is more likely Poisson, misrepresents the true 
likelihood function. In fact, this incorrect 
likelihood, may explain why the constraints on $\alpha$ are less biased for 
the ABC-PMC analysis than the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}
%{\bf \color{darkgreen} CHH: @MJV, I parrot a lot of arguments made in the intro without providing much extra 'meat'. Let me know what you think.  }
